Borel regularity for ODEs and Thimble Integrals

### 2023-12-05 exp-resurgence.tex
Rewrite Section 2.2 Borel regularity for ODEs Rewrite parts of the introduction Add some references

% function spaces
\newcommand{\cont}{\mathcal{C}}
\newcommand{\holo}{\mathcal{H}}
\newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
\newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
\newcommand{\dualsingexp}[2]{\widehat{\mathcal{H}}L^\infty_{#1, #2}}
\newcommand{\dualsingexpalg}[1]{\singexp{#1}{\bullet}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% remove once we stop using old arguments

@@

The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag. 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
%
\begin{equation*}
I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
\end{equation*}
where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.  
\end{enumerate}
These two problems are closely linked. By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.

@@

First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.

Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain. 
\subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).

\begin{verify}
    Turn the ODE into a system: assume 
    \begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame. \textcolor{orange}{Add that the formal series is $1$-Gevrey.}
\color{gray}
Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}). Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).\color{black} Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form 
\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}
labeled by the roots of $P$. This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$. 
At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.
\color{Maroon}
\begin{theorem}
For each root $\alpha$ of $P$,
\end{theorem}
\color{black}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\subsubsection{Why does Borel summation work for thimble integrals?}
Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form 
\[
I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
\]
regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).

Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself. We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}}

\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}
Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}\label{eqn:formula}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}
The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]
On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same. In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
%% the following remark has been moved to Section of the proof
%\begin{remark}\label{rmk:Pham formula}
%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$. When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as 
%    \begin{equation}\label{eqn:Pham}
 %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
 %   \end{equation}
%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
 %  \begin{equation*}
  %     \delta^{-\alpha}:=\begin{cases}

>>>>

% domains
\newcommand{\dualsector}[2]{\Omega_{#1|#2}}

% function spaces
\newcommand{\cont}{\mathcal{C}}
\newcommand{\holo}{\mathcal{H}}
\newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
\newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
\newcommand{\dualsingexp}[2]{\widehat{\mathcal{H}}L^\infty_{#1, #2}}
\newcommand{\dualsingexpalg}[1]{\dualsingexp{#1}{\bullet}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% remove once we stop using old arguments

@@

The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag. 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
%
\begin{equation*}
I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
\end{equation*}
where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex manifold, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.  
\end{enumerate}
These two problems are closely linked. By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.

@@

First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself. \textcolor{Maroon}{[In other words, we go directly from the frequency--analytic quadrant to the position--analytic quadrant, without passing through the formal side.]}

Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain. 
\subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}

Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.

\color{Goldenrod}
[These details are right above in Section~\ref{borel-reg:explanatory-power}!]
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
\color{black}
\begin{verify}
    Turn the ODE into a system: assume 
    \begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

\color{gray}
[This is now a corollary; moved to historical.] Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame. \textcolor{orange}{Add that the formal series is $1$-Gevrey.} Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}). Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). \color{black} \color{Goldenrod}[Let's try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form 
\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}
labeled by the roots of $P$. This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$. 
At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.\color{black}
\textcolor{Cyan}{Using the dictionary for the Laplace transform associated with some point $\zeta = \alpha$ in the frequency domain, (link section), we can turn $\mathcal{P}$ into an integral operator $\hat{\mathcal{P}}_\alpha$. If we choose $-\alpha$ to be a root of $P$, then $\hat{\mathcal{P}}_\alpha$ will have a regular singularity at $\zeta = \alpha$, and we understand a lot of details about its specific form~\cite{reg-sing-volterra}. We show in~\cite{reg-sing-volterra} that $\hat{\mathcal{P}}_\alpha \phi = 0$ has a distinguished solution $\psi_\alpha$ which is characterized by having a power-law singularity with a known exponent $\tau_\alpha - 1$ at $\zeta = \alpha$ and having exponentially bounded growth at infinity.}

We know from experience that we can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions. However, this only works when there's a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$. Why?

A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_\alpha^\theta \phi$ of a function on $\phi$ the position domain. In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$. Because this solution is so unique, its Laplace transform $\Phi_\alpha$ turns out to be Borel regular.

%%The Laplace transform commutes this distinguishing behavior into asymptotics at $z = \infty$, which can be recognized even if we turn $\Phi$ into a formal series $

%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
\color{Maroon}
\begin{theorem}\label{thm:borel_reg_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
\begin{corollary}\label{cor:borel_reg_ODE}
For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\end{corollary}
\color{black}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
\color{Goldenrod}
In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\color{black}
We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}). On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

\begin{center}
\begin{tikzcd}
& & \text{ODE }\arrow[dd,"\laplace^{-1}",swap] & & \\
 {\Psi}_\alpha\arrow[urr, no head, tail] & & & & \tilde{\Psi}_\alpha\arrow[llu,"\text{formal}",swap, no head, tail]\arrow[dd,"\borel"]\\
& & \text{IE} & & \\
\psi_\alpha\arrow[urr, no head, tail]\arrow[uu,"\laplace"]\arrow[r,equal] & \hat{\psi}_\alpha & & & \tilde{\psi}_\alpha\arrow[llu, no head, tail]\arrow[lll,"\text{sum}"]
\end{tikzcd}
\end{center}

Conversely, on the left-hand side, by our existence and uniqueness result \cite[Theorem 4]{reg-sing-volterra} we have an analytic function $\psi_\alpha$ with a distinguished behaviour near $\zeta=\alpha$, which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}). The key step is then comparing $\psi_\alpha$ and $\tilde{\psi}_\alpha$. First, by the properties of the Borel transform, it is easy to show that $\series{\psi}_\alpha$ is a formal solution of the integral equation (IE). Then, from the explicit formula for $\tilde{\Psi}_\alpha$, we can show that if $\tilde{\psi}_\alpha$ grows as $\psi_\alpha$ near $\zeta=\alpha$. Therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\tilde{\psi}_j$ is indeed summable and ${\psi}_\alpha$ is the analytic continuation of $\tilde{\psi}_\alpha$.

\subsubsection{Why does Borel summation work for thimble integrals?}
\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
\color{Goldenrod}
Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form 
\[
I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
\]
regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).

Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself. We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
\color{black}
We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}}
